Supplementary materials

### 2018-02-20 publication/supp_info.Rmd
Add wilcox results tables

```{r}
loadd(dep_frame, sites, consp_self)
```

```{r variation across sites, results='asis'}
consp_self %>%
  anova(test = "Chisq")  %>%
  xtable(caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).  Density were modelled using a quasipoisson distribution. The model suggests that self-pollination rates are species dependent but not across.')
```

>>>>

```{r table species gain global, results = 'asis'}
loadd(significant_gain_global, significant_gain_site, sites)
glance_table(significant_gain_global) %>%
  `rownames<-`(.$recipient) %>%
  select(estimate, statistic, p.value) %>%
  rename(`p value` = p.value,
         `difference` = estimate) %>%
  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. ") %>%
  print(sanitize.rownames.function = function(x) paste0('{\\emph{ ', x, '}}'))
```

```{r table species gain site, results = 'asis'}
loadd(significant_gain_global, significant_gain_site, sites)
glance_table(significant_gain_site) %>%
  inner_join(sites, by = "site_name") %>%
  mutate(site_name = paste(locality_name, land_use, fragment, sep = ' - '),
         rowname = paste0('{\\emph{ ', recipient, '}} - ', site_name)) %>%
  `rownames<-`(.$rowname) %>%
  select(estimate, statistic, p.value) %>%
  rename(`p value` = p.value,
         `difference` = estimate) %>%
  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. ") %>%
  print(sanitize.rownames.function = function(x) x)
```

```{r variation across sites, results='asis'}
loadd(consp_self)
consp_self %>%
  anova(test = "Chisq")  %>%
  xtable(caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).  Density were modelled using a quasipoisson distribution. The model suggests that self-pollination rates are species dependent but not across.')
```
